% Supply PDF metadata.
\begin{filecontents*}{\jobname.xmpdata}
  \Title{Tom Dobson · Curriculum Vitae}
  \Author{T. M. Dobson}
  \Language{en-GB}
  \Keywords{Tom M. Dobson\sep Tom Dobson\sep Curriculum Vitae\sep CV\sep Résumé\sep Resume\sep Resumé\sep Data\sep Consultant\sep Analytics Engineer\sep Analyst\sep Developer\sep Tableau\sep SQL\sep Alteryx\sep Python\sep Power BI\sep dbt}
  \Subject{Professional CV highlighting experience in data analytics and consulting.}
\end{filecontents*}

\PassOptionsToPackage{dvipsnames}{xcolor}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

% Set the page layout.
\geometry{left=1.25cm,right=1.25cm,top=1.25cm,bottom=1.25cm,columnsep=0.85cm,footskip=2\baselineskip}

% Use paracol package to typeset columns in parallel.
\usepackage{paracol}

\usepackage{microtype}

% Set the fonts, taking into account the current compiler.
% To compile with XeLaTeX please use: 
% xerlatex -shell-escape -output-driver="xdvipdfmx -z 0" tom-dobson-cv.tex
\ifxetexorluatex
% If using XeLaTeX or LuaLaTeX:
  \setmainfont{Source Sans Pro}
  \setsansfont{Source Sans Pro}
  \renewcommand{\familydefault}{\sfdefault}
\else
% If using pdfLaTeX:
  \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Set the colours.
\definecolor{DimGrey}{HTML}{696969}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{Black}{HTML}{000000}
\colorlet{name}{Black}
\colorlet{tagline}{Black}
\colorlet{heading}{Black}
\colorlet{headingrule}{LightGrey}
\colorlet{subheading}{SlateGrey}
\colorlet{accent}{SlateGrey}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

% Adjust the fonts.
% \renewcommand{\namefont}{\Huge\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize\bfseries}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the marks used for itemize bullets, \cvskill ratings, and \cvevent date and location.
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}
\renewcommand{\cvLocationMarker}{\faMapMarker*}
% \renewcommand{\cvDateMarker}{\faCalendar*[regular]}

%% Use BibLaTeX to handle citations and set .bib file.
\usepackage[backend=biber,style=science,hyperref=true,abbreviate=true,date=year,sorting=none,autocite=footnote,autopunct=true]{biblatex}
\addbibresource{tom-dobson-cv.bib}

\makeatletter
\def\footnoterule{%
\kern-3\p@
\hbox{%
  \tikz \fill[color=LightGrey]
      (0,0) rectangle (1in,.6pt);%
}%
\kern 2.6\p@\vskip2pt}
\makeatother

\begin{document}
\name{Tom M. Dobson}
\personalinfo{
  \email{dobs.tx@gmail.com}\par
  \linkedin{dobsontom}
  \hfill\location{London, UK}\par
  \github{dobsontom}
  \hfill\phone{+44 (0)7968 673704}
}

\makecvname

% Reduce the size of fonts in itemize environments.
\AtBeginEnvironment{itemize}{\small}

% Set the left:right column width ratio (default 6:4).
\columnratio{0.65}

% Start a two-column paracol.
\begin{paracol}{2}
\cvsection{Experience}

\customcvevent{Analytics Consultant}{The Information Lab}{Apr 2022 -- Present}{London}
\begin{itemize}
\item Completed an intensive, highly competitive, four-month training programme at a leading data analytics consultancy, specialising in Tableau, SQL, Alteryx, PowerBI, and Python.
\item Automated an internal process to detect new client opportunities in Notion and generate supporting documentation, directly saving \textbf{0.25 FTE} and eliminating human error.
\item Designed and implemented an automatic system to detect new Tableau User Group events online and post alerts to an internal network using Python, GitHub Actions, Zapier, and Snowflake.
\item Conducted two years of technical consulting at Inmarsat, IAG Cargo, and the BBC as detailed below.
% \item Delivered in-person and online training in Tableau and Alteryx across a number of clients and sectors, including the University of Hertfordshire.
% Developed skills in stakeholder management, documentation authorship and maintenance, and version-control.

\medskip
\cvtag{Tableau}
\cvtag{Snowflake}
\cvtag{Alteryx}
\cvtag{Python}
\cvtag{PowerBI}
\cvtag{Zapier}

\end{itemize}

\divider

% \cvsection{Consulting}

\customcvevent{Insight Analyst}{Inmarsat}{Jan 2024 -- Present}{London}
\begin{itemize}
\item Designed and deployed a revenue protection system using SQL and Tableau to identify contracts approaching their end of commitment date, exposing \textbf{£2.9m} in annualised revenue at risk in April 2024.
\item Created SQL queries to scaffold, unify, and standardise more than ten tables of product performance data into a single source of truth. Designed an optimised Tableau front-end to alert the business of performance changes and issues in source tables, resulting in significant time savings.

% \scriptsize
% \begin{center}\textit{"I think this may be the best dashboard I have ever seen come from within our own ranks."}\\Chuck Mosely, Sales Director\end{center}
% \normalsize

\medskip
\cvtag{Tableau}
\cvtag{BigQuery}
\cvtag{GoogleSQL}
\cvtag{Alteryx}
\cvtag{ADF}

\end{itemize}

\divider

\customcvevent{Advanced Analytics \& Reporting Analyst}{IAG Cargo}{Feb 2023 -- Aug 2023}{London}
\begin{itemize}
\item Developed and productionised SQL procedures and a Tableau front-end to intelligently distribute warehouse tasks between employees based on resource availability and task complexity, directly enabling a reduction in headcount and saving \textbf{1 FTE}.
\item Designed and deployed an automated system in Oracle to expose \textbf{£98k} in incorrectly declared cargo in 2023. Enabled recuperation of lost revenue via automated reporting of incidents through BusinessObjects.
\item Performed a full audit of an undocumented database to determine its capacity to enhance performance monitoring for business operations, presenting findings to senior stakeholders.
\item Scoped and re-engineered Oracle database schema to eliminate errors when calculating business-critical flight performance metrics, tested changes in parallel, and oversaw migration to the new design.
% \item Implemented a CO\textsubscript{2} monitoring pipeline to enable the calculation of customer emissions profiles ( ... ) .

\medskip
\cvtag{Tableau}
\cvtag{Oracle}
\cvtag{PL/SQL}
\cvtag{BusinessObjects}

\end{itemize}

\divider

\customcvevent{Tableau \& Alteryx Consultant}{British Broadcasting Corporation (BBC)}{Jul 2022 -- Jan 2023}{London}
\begin{itemize}
\item Designed and implemented data pipelines in Alteryx to clean and combine over six million rows of survey data. Produced an accompanying Tableau front-end to aggregate information into a single source of truth.
\item Automated the creation and delivery of daily reports on high-performing news stories to senior stakeholders using Alteryx.
% \item Collaborated with internal and external stakeholders to construct a dashboard supporting a global understanding of brand perception. 
% \item Built a Tableau dashboard to highlight articles and themes with consistent and long-lasting traffic to guide content creation.

\medskip
\cvtag{Tableau}
\cvtag{PostgreSQL}
\cvtag{Alteryx}

\end{itemize}

%% Switch to the right column.
\switchcolumn

\cvsection{Contact}
\makecvinfo

\cvsection{Skills}
\cvskill{Tableau}{5}
\cvskill{Alteryx}{5}
\cvskill{SQL}{4}
\cvskill{Python}{3}
\cvskill{Power BI}{3}
% \small{$\bullet$  = Proficient\hfill 
% $\bullet$$\bullet$$\bullet$$\bullet$$\bullet$ = Expert}\\

\divider
\\\textbf{\faDatabase \:Databases}\\
\medskip
\cvtag{BigQuery}
\cvtag{Snowflake}
\cvtag{PostgreSQL}
\\\smallskip
\cvtag{Oracle 11\textit{g}}
\cvtag{MS SQL Server}

\divider

\textbf{\faGithub \:Management}\\
\medskip
\cvtag{GitHub}
\cvtag{Jira}
\cvtag{Notion}

\divider

\textbf{\faCogs \:Data Engineering}\\
\medskip
\cvtag{SQL}
\cvtag{Python}
\cvtag{PowerShell}
\cvtag{Git}

\divider

\textbf{\faFlask \:Data Science}\\
\medskip
\cvtag{Jupyter}
\cvtag{NumPy}
\cvtag{pandas}
\cvtag{VS Code}

\cvsection{Certifications}
\smallskip
\cvachievement{./icons/alteryx-logo.pdf}{Alteryx Designer Advanced}{Mar 2024}{}
\cvachievement{./icons/pbi-logo.pdf}{Power BI Data Analyst Associate}{Oct 2023}{}
\cvachievement{./icons/tableau-logo.pdf}{Tableau Certified Data Analyst}{Aug 2023}{}

\cvsection{Education}
\cvevent{MSc (R) Biological Sciences}{University of Bristol}{Sep 2016 -- Aug 2021}{}
\small
\faGraduationCap \;First Class Hons. (BSc)
\smallskip
\\ \faTrophy \;Nominee · Best PhD\hspace{0.5pt}/\hspace{0.5pt}MSc Thesis\footfullcite{dobson2022}
\\\medskip
\cvtag{Python}
\cvtag{R}
\cvtag{SPSS}
\cvtag{\LaTeX}

\end{paracol}
\end{document}
