\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
%% AltaCV uses the fontawesome5 and packages.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1cm,right=1cm,top=1.25cm,bottom=1.25cm,columnsep=0.8cm,footskip=2\baselineskip}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
% WHEN COMPILING WITH XELATEX PLEASE USE
% xelatex -shell-escape -output-driver="xdvipdfmx -z 0" sample.tex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  %\usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{DimGray}{HTML}{696969}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{Black}{HTML}{000000}
\colorlet{name}{Black}
\colorlet{tagline}{Black}
\colorlet{heading}{Black}
\colorlet{headingrule}{LightGrey}
\colorlet{subheading}{SlateGrey}
\colorlet{accent}{SlateGrey}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}
% ...and the markers for the date/location for \cvevent
% \renewcommand{\cvDateMarker}{\faCalendar*[regular]}
\renewcommand{\cvLocationMarker}{\faMapMarker*}

\begin{document}
\name{Tom Dobson}
\personalinfo{%
  \email{dobs.tx@gmail.com}
  \hfill\location{London, UK}
  \\\linkedin{tomdobs}
  \hfill\phone{+44 (0)7968 123456}
  \\\github{tomdobs}
}

\makecvname
%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.65}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.

\begin{paracol}{2}
\cvsection{Experience}

\cvevent{Data Consultant}{The Information Lab}{Apr 2022 -- Present}{London}
\begin{itemize}
\item Completed an intensive, highly competitive, four-month training programme at one of the UK’s leading data analytics consultancy firms.
\item Automated an internal client management process, involving the detection of new opportunities in Notion and the generation of accompanying documentation, saving approximately 0.25 FTE and eliminating human error.
\item Designed and implemented an automated system to detect new Tableau User Group postings and post alerts to an internal network using Python, GitHub Actions, Zapier, and Snowflake.
\item Conducted two years of technical consulting in SQL, Tableau, Alteryx, and Python at the following organisations:
% \item Delivered in-person and online training in Tableau and Alteryx across a number of clients and sectors, including the University of Hertfordshire.
% Developed skills in stakeholder management, documentation authorship and maintenance, and version-control.

\medskip
\cvtag{Tableau}
\cvtag{SQL}
\cvtag{Alteryx}
\cvtag{Python}
\cvtag{PowerBI}
% \cvtag{Zapier}

\end{itemize}

\divider

\cvevent{Insight Analyst}{Inmarsat}{Jan 2024 -- Present}{London}
\begin{itemize}
\item Designed and deployed a revenue protection system using SQL and Tableau to identify customers that are approaching their contract's end of commitment date, exposing \$3.7m in annualised revenue at risk in April 2024 alone.
% \scriptsize
% \begin{center}\textit{"I think this may be the best dashboard I have ever seen come from within our own ranks."}\\Chuck Mosely, Sales Director\end{center}
% \normalsize

\medskip
\cvtag{Tableau}
\cvtag{BigQuery}
\cvtag{Alteryx}
\cvtag{ADF}

\end{itemize}

\divider

\cvevent{Advanced Analytics \& Reporting Analyst}{IAG Cargo}{Feb 2023 -- Aug 2023}{London}
\begin{itemize}
\item Developed and productionised solutions in Oracle and Tableau to intelligently distribute tasks between warehouse employees based on resource availability and task complexity, enabling significant time savings.
\item Designed and implemented an automated system using SQL and Tableau to identify incorrectly declared cargo. Enabled recuperation of lost revenue via automated reporting of offending clients via SAP BusinessObjects.
\item Performed a full audit of an undocumented database to determine its suitability for answering a range of business questions, presenting findings to senior stakeholders.
\item Scoped and re-engineered an Oracle database schema to prevent errors when calculating business-critical metrics (what metric??), tested changes in parallel, and oversaw migration to the new design.
\item Implemented a CO\textsubscript{2} monitoring pipeline to enable the calculation of customer emissions profiles ( ... ) .

\medskip
\cvtag{Tableau}
\cvtag{SQL}
\cvtag{Alteryx}

\end{itemize}

\divider

\cvevent{Tableau \& Alteryx Consultant}{British Broadcasting Corporation (BBC)}{July 2022 -- Jan 2023}{London}
\begin{itemize}
\item Designed ETL pipelines in Alteryx to combine and standardise big data from a variety of different sources.
\item Collaborated with internal and external stakeholders to construct a dashboard to support a global understanding of band perception. 
\item Automated the delivery of daily reports of the best performing news stories to senior stakeholders.
\item Built a Tableau dashboard to highlight articles and themes that receive consistent and long-lasting traffic to guide content creation.

\medskip
\cvtag{Tableau}
\cvtag{PostgreSQL}
\cvtag{Alteryx}

\end{itemize}

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Contact}
\makecvinfo

\cvsection{Education}
\cvevent{MSc. (R) Biological Sciences}{University of Bristol}{Sep 2016 -- Aug 2021}{}
\small
\faGraduationCap \;First Class Hons. (BSc.)
\smallskip
\\ \faTrophy \;Nominee · Best Postgraduate Thesis
\\\medskip
\cvtag{Python}
\cvtag{R}
\cvtag{SPSS}
\cvtag{\LaTeX}

\cvsection{Skills}
\cvskill{Tableau}{5}
\cvskill{Alteryx}{5}
\cvskill{SQL}{4}
\cvskill{Python}{3}
\cvskill{Power BI}{3}
% \small{$\bullet$  = Proficient\hfill 
% $\bullet$$\bullet$$\bullet$$\bullet$$\bullet$ = Expert}\\

\divider
\\\textbf{\faDatabase \:Databases}\\
\medskip
\cvtag{BigQuery}
\cvtag{Snowflake}
\\\smallskip
\cvtag{Oracle 11\textit{g}}
\cvtag{MS SQL Server}

\divider

\textbf{\faGithub \:Management}\\
\medskip
\cvtag{GitHub}
\cvtag{Jira}
\cvtag{Notion}

\divider

\textbf{\faCogs \:Data Engineering}\\
\medskip
\cvtag{SQL}
\cvtag{Python}
\cvtag{PowerShell}
\cvtag{Git}

\divider

\textbf{\faFlask \:Data Science}\\
\medskip
\cvtag{Jupyter}
\cvtag{NumPy}
\cvtag{pandas}
\cvtag{VS Code}

\cvsection{Certifications}
% \cvevent{}{\normalfont Alteryx Designer Advanced Certified}{March 2024}{}
% \cvevent{}{\normalfont Microsoft Certified: Power BI Data\\Analyst Associate}{October 2023}{}
% \cvevent{}{\normalfont Tableau Certified Data Analyst}{August 2023}{}

\cvachievement{./icons/alteryxLogo.pdf}{Alteryx Designer Advanced Certified}{March 2024}{}
\cvachievement{./icons/pbiLogo.pdf}{Power BI Data Analyst Associate}{October 2023}{}
\cvachievement{./icons/tableauLogo.pdf}{Tableau Certified Data Analyst}{August 2023}{}

\end{paracol}
\end{document}
